Autonomous Quadrotor Landing on a Moving Platform

### 2016-04-22 docs/report/report.tex
Minor edits

\subsection{Related Work}
The autonomous landing problem can be thought of as a set of three separate control problems or stages. First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods. Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory. Once the quad has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.

From the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor. In the work of Kim, 2014 \cite{Kim2014} a basic color threshold technique was to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide the state estimations. In the work of Heriesse Et al. \cite{Herisse2012} an optical flow technique was applied to a series of images captured on board the quadrotor to estimate the require state estimation in order to control the quad rotor and conduct autonomous landing. While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting there general applicability.

In the case of Ling \cite{Kim2014}, the brightness used in his thresholding techquie must be set ahead of time and is sensitve to lighting changes and a similar issue is noted in the work of Heriesse \cite{Herisse2012}. Moreover in the work of Lim, there are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed. This means that as the quadrotor approach the landing pad, it tends to lose any measurements of its state and therefore must complete the final landing procedure by propagating the last measured state forward.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
		\caption{}

	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
		\caption{}

	\end{subfigure}
	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
	\label{fig:AprilTag_eval}	
\end{figure}

@@

It is suspected that the PointGrey Camera used in this test was not operating at the requested frame rate of 60 fps. This was not noted until after analysising the data and will be investigated this coming week. In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resting the frame rate from 30 fps to 60 fps with no warning or indication. If this is the case, then the update rate of the AprilTag library on the Odroid may actually be faster than what is shown in Figure \ref{fig:AprilTag_eval}. In cases where a more powerful computer can be used, the adaptive image processing method results in the AprilTag library operating at 60 fps with no delay, making it extremely useful on machines that can leverage greater computational power.

@@

From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} that the roll and pitch commands are bounded to $\pm 20^o$ further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds. Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time. A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.

@@

These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered far to aggressive for the quadrotor used in these experiments. Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees. Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag directly and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag. Such a test will be the focus of the majority of effort in the coming weeks.

@@

\section{Conclusions and Future Work}
A set of algorithms were developed to provide fast, reliable and accurate estimations of state between a landing pad and a quadrotor using a series of image preprocessing methods and the MIT AprilTags library. These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power onboard, quadrotor mounted computer system. A set of PID controllers were developed, tested and evaluated using the same motion capture system to provide state estimates and a ground truth. A set of stable yet responsive PID gains were found and tested using this system and an evaluation of their behaviour in the presence of large disturbances was conducted.

In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure. Once such a landing can be performed consistently in the face of minor disturbances it, the same procedure will be applied to quadrotor and landing system where the landing platform will be mounted to a moving vehicle.

>>>>

\subsection{Related Work}
The autonomous landing problem can be thought of as a set of three separate control problems or stages. First the quadrotor must detect the relative position and velocity of the landing target using either GPS of visual methods. Next the quadrotor must determine a rendezvous location with the landing target and plan the required flight trajectory. Once the quadrotor has rendezvoused a final landing trajectory must be calculated between quadrotor and the landing pad.

From the perception portion of the problem there have been two main techniques use to identify the landing pad and estimate its state relative to the quadrotor. In the work of Kim, 2014 \cite{Kim2014} a basic color threshold technique was to identify the landing target and the MIT AprilTags library \cite{apriltags} was used to provide the state estimations. In the work of Heriesse Et al. \cite{Herisse2012} an optical flow technique was applied to a series of images captured on board the quadrotor to estimate the require state estimation in order to control the quad rotor and conduct autonomous landing. While both of these techniques have been shown to work in very specific cases both require case specific parameters to be applied ahead of time, thereby limiting their general applicability.

In the case of Ling \cite{Kim2014}, the brightness used in his thresholding techquie must be set ahead of time and is sensitve to lighting changes and a similar issue is noted in the work of Heriesse \cite{Herisse2012}. There are also implementation issues due to the slow state estimation rate of the AprilTag library and the issue of the AprilTags falling out of view of the camera during the final stages of decent were not addressed. This means that as the quadrotor approach the landing pad, it tends to lose any measurements of its state and therefore must complete the final landing procedure by propagating the last measured state forward.

@@

\begin{figure}	
	\centering
	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_FPS_vs_Dist.eps}
	\end{subfigure}

	\begin{subfigure}[b]{\linewidth}
		\includegraphics[width=\textwidth]{images/Apr_Distance_Error.eps}
	\end{subfigure}
	\caption{Evaluation of AprilTag state estimation and update rate as functions of distance}
	\label{fig:AprilTag_eval}	
\end{figure}

@@

It is suspected that the PointGrey Camera used in this test was not operating at the requested frame rate of 60 fps. This was not noted until after analysising the data and will be investigated this coming week. In the past there have been problems with the PointGrey camera changing its settings after several reboots, often resetting frame rate from 30 fps to 60 fps with no warning or indication. If this is the case, then the update rate of the AprilTag library on the Odroid may actually be faster than what is shown in Figure \ref{fig:AprilTag_eval}. In cases where a more powerful computer can be used, the adaptive image processing method results in the AprilTag library operating at 60 fps with no delay, making it extremely useful on machines that can leverage greater computational power.

@@

From Figures \ref{fig:pid_roll_command} and \ref{fig:pid_pitch_command} the roll and pitch commands were bounded to $\pm 20^o$, further more when the quadrotor is perturbed in any direction the position controller has been able recover within 2-4 seconds. Same applies to the thrust commands, when altitude is perturbed the quadrotor is able to self correct to the desired altitude with time. A video of the plotted dataset can be viewed \href{https://www.youtube.com/watch?v=v1QDdZ0LdMc&index=17&list=PLk5z6lLnKFd6BD9EXWa09hqf6SNQhn59R}{here}.

@@

These plots also highlight the need to place a limit on the commanded output as in the roll and pitch PID controllers there were cases where the sum of the derivative term with the proportional and integral error terms may lead to a commanded pitch or roll greater than 60 degrees which is considered too aggressive for the quadrotor used in these experiments. Further tuning and testing of the PID controller will be carried out in the coming weeks along with tests that do not require the yaw to be stabilized at zero degrees. Theoretically it will be possible to directly apply the PID controllers to state estimates obtained by the AprilTag and in such cases it should be possible to use these same controllers to follow and land on a moving AprilTag target.

@@

\section{Conclusions and Future Work}
A set of algorithms were developed to provide fast, reliable and accurate estimations of state between a landing pad and a quadrotor using a series of image preprocessing methods and the MIT AprilTags library. These methods were tested and evaluated using a motion capture system to provide ground truth and were shown to provide update rates of greater than 20 Hz for a low power, onboard quadrotor mounted computer system. A set of PID controllers were developed, tested and evaluated using the same motion capture system to provide state estimates and a ground truth. A set of stable yet responsive PID gains were found and tested using this system and an evaluation of their behaviour in the presence of large disturbances was conducted.

In the coming weeks the state estimates used by the PID controllers will be provided solely by an AprilTag located on the ground and a series of procedures using these controllers will be derived such that the quadrotor will hover over the AprilTag before initializing a landing procedure. Once such a landing can be performed consistently in the face of minor disturbances, the same procedure will be applied to a quadrotor and landing system where the landing platform will be mounted to a moving vehicle.
